Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-22 draft.tex
merge

\begin{proof}
\brian{we should just cite our paper with Eugene for this, with a few comments about what changes}
Suppose $V \times [0,\epsilon) \subset M \times \RR_{\geq 0}$ is an open set. 
Then, as cochain complexes 
\[
\clie^\bu(\cL(V \times [0,\epsilon)) = {\rm Sym} \left(\Bar{\Omega}^\bu_c(V \times [0,\epsilon) [2] \right)  .
\]
Here $\Bar{\Omega}^\bu_c$ denotes the compactly supported distributional de Rham forms. 
By ellipticity, the inclusion $\Omega^\bu \hookrightarrow \Bar{\Omega}^\bu_c$ is a quasi-isomorphism which induces a quasi-isomorphism
\[
\bC_n(\fg) (V \times [0,\epsilon)) \hookrightarrow \clie^\bu(\cL(V \times [0,\epsilon)) 
\]
as desired. 
The quasi-isomorphism for the value of the factorization algebras on open sets $U \subset M \times \RR_{>0}$ is defined similarly. 
\end{proof}

>>>>

\begin{proof}
\brian{all we need to say is that half-smeared is equivalent to full observables}

%Suppose $V \times [0,\epsilon) \subset M \times \RR_{\geq 0}$ is an open set. 
%Then, as cochain complexes 
%\[
%\clie^\bu(\cL(V \times [0,\epsilon)) = {\rm Sym} \left(\Bar{\Omega}^\bu_c(V \times [0,\epsilon) [2] \right)  .
%\]
%Here $\Bar{\Omega}^\bu_c$ denotes the compactly supported distributional de Rham forms. 
%By ellipticity, the inclusion $\Omega^\bu \hookrightarrow \Bar{\Omega}^\bu_c$ is a quasi-isomorphism which induces a quasi-isomorphism
%\[
%\bC_n(\fg) (V \times [0,\epsilon)) \hookrightarrow \clie^\bu(\cL(V \times [0,\epsilon)) 
%\]
%as desired. 
%The quasi-isomorphism for the value of the factorization algebras on open sets $U \subset M \times \RR_{>0}$ is defined similarly. 
\end{proof}
